Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-05 inspiral_svd.tex
Improved short title
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@940 ccdd05d5-56c1-461a-bf98-85f6876523b4

\title[LLOID]{Technique for \earlywarning\ detection of compact binary
coalescence and its implications for multi-messenger astronomy}

>>>>

\title[Early-warning detection of compact binary coalescence]{Technique for \earlywarning\ detection of compact binary
coalescence and its implications for multi-messenger astronomy}
